Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum disks

### 2018-11-21 paper_prd.tex
some changes, more to come

Therefore, we compute the mass of the tori around KBHsSH and, for comparison, the corresponding mass for seven disk models around Kerr BHs, each one of them with the same ADM quantities as their KBHsSH counterparts. The resulting values are reported in 
Table~\ref{density_table}. The variables corresponding to the Kerr case are indicated with a `K' superindex in this table. The fourth  and seventh columns of Table~\ref{density_table} indicate the resulting central densities for the KBHsSH and Kerr BH cases, respectively, in geometrized units. In order to compare these values with those from the end-products of binary neutron star mergers, we need to convert our results to cgs units. To this end, we first need to choose a mass for the scalar field $\mu$, as the maximum ADM mass of KBHsSH depends on $\mu$. In particular, we compute the maximum ADM mass with the following equation (see~\cite{Herdeiro:2015a} and references therein)
\begin{equation}\label{eq:max_mass_HBH}
M^{\rm max}_{\rm ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{\mathrm{GeV}}{\mu}\right)\,
\end{equation}
for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$). The constant $\alpha_{\mathrm{BS}}$ is computed numerically for rotating boson stars. Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the mass for the corresponding KBHsSH.
\tf{I don't find this formula in reference~\cite{Delgado:2018}. Are you sure the formula is well written? The dimensions look strange. What is $\alpha_{\mathrm{BS}}$?}
Using a value of the mass of the scalar field of $\mu = 2.087 \times 10^{-11}$ eV yields values for the ADM mass of our models that increase from 2.043 $M_{\odot}$ to 4.799 $M_{\odot}$, from model I to VII. Note that, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories. \sg{not sure about this last comment, but I think something should be told about $\mu$.} \tf{Yes, but probably is not the best reference since it is not GR.}. Finally, we use the following equation
\begin{equation}
\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}\,
\end{equation}
to compute the cgs value of the central density for the different models.

>>>>

Therefore, we compute the mass of the tori around KBHsSH and, for comparison, the corresponding mass for seven disk models around Kerr BHs, each one of them with the same ADM quantities as their KBHsSH counterparts. The resulting values are reported in 
Table~\ref{density_table}. The variables corresponding to the Kerr case are indicated with a `K' superindex in this table. The fourth  and seventh columns of Table~\ref{density_table} indicate the resulting central densities for the KBHsSH and Kerr BH cases, respectively, in geometrized units. In order to compare these values with those from the end-products of binary neutron star mergers, we need to convert our results to cgs units. To this end, we first need to choose a mass for the scalar field $\mu$, as the maximum ADM mass of KBHsSH depends on $\mu$. In particular, we compute the maximum ADM mass with the following equation (see~\cite{Herdeiro:2015a} and references therein)
\begin{equation}\label{eq:max_mass_HBH}
M^{\rm max}_{\rm ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{\mathrm{GeV}}{\mu}\right)\,
\end{equation}
\sg{for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$). The constant $\alpha_{\mathrm{BS}}$ is computed numerically for rotating boson stars. Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the mass for the corresponding KBHsSH.}
\tf{I don't find this formula in reference~\cite{Delgado:2018}. Are you sure the formula is well written? The dimensions look strange. What is $\alpha_{\mathrm{BS}}$?}
Using a value of the mass of the scalar field of $\mu = 2.087 \times 10^{-11}$ eV yields values for the ADM mass of our models that increase from 2.043 $M_{\odot}$ to 4.799 $M_{\odot}$, from model I to VII. This value of $\mu$ is within the mass range suggested by the \emph{Axiverse} of string theory (see~\cite{Arvanitaki:2010}) (a large number of scalar fields in a mass range from $10^{-33}$ eV to $10^{-10}$ eV). In addition, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories (Although in this work we are working with GR, for the low values of the trace of the energy-momentum tensor $T$ we are working (in comparison with the values reached for neutron stars) both theories should be indistinguishable). \tf{Yes, but probably is not the best reference since it is not GR.}. Finally, we use the following equation (from~\cite{RezzollaBook})
\begin{equation}
\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}\,
\end{equation}
to compute the cgs value of the central density for the different models.
